---
title: "SEC1-SA2-GROUP9-AGUILA,V-MASICAT,L-SA2"
output: html_document
date: "2024-05-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Bitcoin Trading

Find out which probability distribution function best fits Bitcoin’s returns for trading data every minute, from January 1, 2012 to April 15, 2024, for Bitcoin quoted in United States dollars or the BTC/USD pair. 

```{r start}
# Define Tsallis distribution function
rtsallis <- function(n, q, mean, sd) {
  x <- rnorm(n, mean, sd)
  x <- x / sqrt(q)
  return(x)
}

# Load necessary libraries
library(stats)

# Load the CSV file
df <- read.csv("/Users/veraaguila/Downloads/btcusd.csv")
head(df, 10)
# Convert 'Price' column to numeric
df$Price <- as.numeric(as.character(df$Price))

# Create a function to drop NA values and calculate returns
DropNA <- function(x) {
  x <- diff(log(x$Price))
  x <- x[!is.na(x)]
  return(x)
}

# Create random samples for each distribution and perform Kolmogorov-Smirnov tests
distributions <- c("normal", "t", "cauchy", "tsallis", "powerlaw")
results <- data.frame(Distribution = distributions, D_statistic = numeric(length(distributions)))

for (dist in distributions) {
  set.seed(123) # Set seed for reproducibility
  df_teste <- switch(dist,
                     normal = rnorm(length(DropNA(df)), mean = mean(DropNA(df)), sd = sd(DropNA(df))),
                     t = rt(length(DropNA(df)), df = length(DropNA(df)) - 1),
                     cauchy = rcauchy(length(DropNA(df)), location = mean(DropNA(df)), scale = sd(DropNA(df))),
                     tsallis = rtsallis(length(DropNA(df)), q = 2, mean = mean(DropNA(df)), sd = sd(DropNA(df))),
                     powerlaw = poweRlaw::rplcon(length(DropNA(df)), -0.3, sd(DropNA(df))))
  
  
  ks_result <- ks.test(DropNA(df), df_teste)
  results[results$Distribution == dist, "D_statistic"] <- ks_result$statistic
}

# Show the results
results

# Find the distribution with the smallest D_statistic
best_distribution <- results[which.min(results$D_statistic), "Distribution"]
best_statistic <- min(results$D_statistic)

# Print the conclusion
cat("The best-fitting distribution for Bitcoin's returns is", best_distribution, "with a D_statistic of", best_statistic, "\n")

```
```

## Ethereum Trading
Test using Shapiro-Wilk normality test the Ethereum returns for trading data every five minutes, from August 7, 2015 to April 15, 2024.


```{r setup2, include=FALSE}


library(knitr)

library(readr)
library(ggplot2)
library(dplyr)
```

```{r, include=FALSE}

ETHD <- read_csv("/Users/veraaguila/Documents/ETH-USD.csv")
# Remove rows with non-finite values
ETHD <- ETHD[complete.cases(ETHD), ]

str(ETHD)

```

```{r code}
ETHD <- na.omit(ETHD)

summary(ETHD)

ggplot(ETHD, aes(x = Date, y = Close)) +
  geom_line() +
  labs(x = "Date", y = "Price (USD)", title = "Time Series of Ethereum Prices")

ETHD$Return <- c(NA, diff(log(ETHD$Close)))

summary(ETHD$Return)

ggplot(ETHD, aes(x = Return)) +
  geom_histogram(bins = 30, fill = "blue", color = "black", na.rm = TRUE) +
  labs(x = "Return", y = "Frequency", title = "Histogram of Ethereum Returns")

ST <- shapiro.test(ETHD$Return)
print("Shapiro-Wilk Test:")
print(ST)

alpha <- 0.05
if (ST$p.value > alpha) {
  print("The returns are normally distributed (fail to reject H0)")
} else {
  print("The returns are not normally distributed (reject H0)")
}

summTable <- ETHD %>%
  summarize(
    MeanReturn = mean(Return, na.rm = TRUE),
    SDReturn = sd(Return, na.rm = TRUE),
    MinReturn = min(Return, na.rm = TRUE),
    MaxReturn = max(Return, na.rm = TRUE)
  )
kable(summTable)

```